### 2018-12-01 paper/intro.tex
Tweak some of the typesetting
Start over on the paper

In the two decades since they were introduced by \citet{wadler89}, \emph{type classes} have proven a versatile apparatus for structuring programs. Consider a class intended to characterize types $\tVar$ for which a monoid can be defined:
\begin{flalign*}
  & \eClass{\tMonoid{\tVar}} & \\
  & \quad \tAnno{\eIdentity}{\tVar} & \\
  & \quad \tAnno{\eCombine}{\tArrow{\tVar}{\tArrow{\tVar}{\tVar}}} &
\end{flalign*}
Programmers can use this class to define polymorphic functions over all monoids:
\begin{flalign*}
  & \tAnno{\eSquare}{\tMonoid{\tVar} \Rightarrow \tArrow{\tVar}{\tVar}} & \\
  & \eApp{\eSquare}{\eX} = \eApp{\eApp{\eCombine}{\eX}}{\eX} &
\end{flalign*}
Finally, an \emph{instance} of the class can be provided for a specific type:
\begin{flalign*}
  & \eInstance{\tMonoid{\integer}} & \\
  & \quad \eIdentity = \numberName{1} & \\
  & \quad \eCombine = \eMultiply &
\end{flalign*}
where $\tAnno{\numberName{1}}{\integer}$ and $\tAnno{\eMultiply}{\tArrow{\integer}{\tArrow{\integer}{\integer}}}$. The instance is a witness to justify the well-definedness of expressions like $\eApp{\eSquare}{\numberName{3}}$.

More recently, algebraic effects \citep{plotkin03} and handlers \citep{plotkin09} have become an attractive alternative to monads for modeling computational effects due to their compositionality.

>>>>

We call a monad \(\left(T, \eta, \mu\right)\) in a category \(\mathbb{C}\) \emph{algebraic} if every natural transformation \(\varepsilon : T \rightarrow 1_\mathbb{C}\) makes the diagrams

\medskip
\noindent\begin{minipage}{\dimexpr.5\textwidth-.5\columnsep}
  \centering
  \begin{tikzcd}[row sep=huge, column sep=huge]
    1_\mathbb{C} \arrow[r, "\eta"] \arrow[rd, "1"]
      & T \arrow[d, "\varepsilon"] \\
    & 1_\mathbb{C}
  \end{tikzcd}
\end{minipage}\begin{minipage}{\dimexpr.5\textwidth-.5\columnsep}
  \centering
  \begin{tikzcd}[row sep=huge, column sep=huge]
    T^2
        \arrow[r, "\mu"]
        \arrow[d, "\varepsilon T"]
      & T
        \arrow[d, "\varepsilon"]
        \arrow[dl, equal] \\
    T
        \arrow[r, "\varepsilon"]
      & 1_\mathbb{C}
  \end{tikzcd}
\end{minipage}
\medskip

\noindent commute. If \(\left(T, \eta, \mu\right)\) and \(\left(U, \delta, \nu\right)\) are algebraic monads, then any pair of natural transformations \(\varepsilon : T \rightarrow 1_\mathbb{C}\) and \(\theta : U \rightarrow 1_\mathbb{C}\) induces a composite algebraic monad \(\left(T U, \eta U \circ \delta, \theta TU \circ \varepsilon UTU\right)\). Furthermore, \(\delta T \circ \eta \circ \theta \circ \varepsilon U : TU \rightarrow UT\) is a natural isomorphism, which is to say composition of algebraic monads is commutative.
